\textbf{BibTrek Prototype: A Graph Visualization Tool and Search Engine for Cybersecurity Papers}

### 2019-07-26 article/article.tex
Conclusion written and done. Moving to the Related Work

\section{Introduction}
(Quase final. Cortar palavras. Algumas das coisas aqui podem ser usadas como introduções na solução e avaliação)
\subsection{Problem}
As a result of the rising number of cyberattacks, it is becoming hard to find white-hat hackers that know how to thwart these kinds of attacks effectively. However, with the increased availability of information on the web it is becoming easier to study and learn how these attacks work. The cutting edge techniques used to carry them out is mostly found on the latest scientific research papers. Due to the many iterations of scientific knowledge the most recent work builds upon the work that has been done on the past. Because of this, to understand the most recent concepts it is important the reading of the referenced papers that made the writing of the current one possible. With this being said the most relevant paper of a certain subject becomes the paper with more references to it, thus making it an obligatory read. Having said that, the reality is that performing these kinds of bibliography surveys is time-consuming and inefficient.

@@

\section{Related Work}
#Yet to be researched

\section{Solution}
(Sketch)
#Write a brief introduction. Maybe use the text that I used above but here instead
\subsection{Design}
The BibTrek application was written using the Java programming language mainly due to the fact that it is ubiquitous on modern-day computing systems. The database module uses Neo4J and requires us to have either a local or remote instance running it. The connection of the JVM to the Neo4J is made using the BOLT protocol on the network port: 7687. The JSON format was chosen as the way to retrieve the information from the DBLP database using the API due to it being lightweight and having overall great flexibility. The Neo4J database is queried using "
Cypher" which is its standard query language. The application was built using the Maven tool and uses the Neo4J driver and JSON maven repositories. Finally, we use the java.net package in order to establish an HTTP connection with the DBLP API.

@@

\section{Future Work}
The reader of this article has to keep in mind that this project was developed in one month throughout the writer's internship with INESC-ID. Because of this there are many aspects of the current BibTrek implementation that ought to be further engineered and developed. To begin with, one of the obvious aspects to further develop would be to fetch information from more than one web based library. At the current moment only the DBLP is being used. Finally, while the ArXiV API is free to use, IEEE Xplore requires the use of a key attributed to its developers. Another aspect that should be considered is the use of dynamic attributes since, at the moment, any block of data that is fetched has some of its attributes unused because, we adhere to a fixed attribute standard when adding data to the database. At the current moment the only nodes being added to the database are either Authors or Publications. We should consider adding Companies, Foundations, Organizations, Universities and other Institutions that authors are or have been linked with in the past, Keywords/Subjects and any other relevant information for the reader. It is worth being said that nodes being created ought to be the most common set of information between the data that is being stored in the different databases that BibTrek will be using. Finally, along with more diverse nodes, each one of them should have a vast array of arguments in order to better categorize the information being added. Furthermore, at the current moment BibTrek allows the user to add duplicated information. Obviously a check should be added in the Java code that compares if the information that is trying to be added has been put there already. Finally, we are not able to query our Neo4J graph database through the terminal console. The work to be done regarding this topic is developing the option of querying the database through a user input choice from a vast array of specific functions that manipulate the information present there, displaying relevant information about the current status of the data to the user we the intent on aiding its research process. An example of a query would be getting the most referenced paper by all the papers presently on the database with respect to a certain subject or given the current paper title that references one of the said papers.

>>>>

\section{Introduction}
%(Quase final. Cortar palavras. Algumas das coisas aqui podem ser usadas como introduções na solução e avaliação)
\subsection{Problem}
As a result of the rising number of cyberattacks, it is becoming hard to find white-hat hackers that know how to thwart these kinds of attacks effectively. However, with the increased availability of information on the web it is becoming easier to study and learn how these attacks work. The cutting edge techniques used to carry them out is mostly found on the latest scientific research papers. Due to the many iterations of scientific knowledge the most recent work builds upon the work that has been done on the past. Because of this, to understand the most recent concepts it is important the reading of the referenced papers that made the writing of the current one possible. With this being said the most relevant paper of a certain subject becomes the paper with more references to it, thus making it an obligatory read. Having said that, the reality is that performing these kinds of bibliography surveys is time-consuming and inefficient.

@@

\section{Related Work}
%#Yet to be researched

\section{Solution}
%(Sketch)
%#Write a brief introduction. Maybe use the text that I used above but here instead
\subsection{Design}
The BibTrek application was written using the Java programming language mainly due to the fact that it is ubiquitous on modern-day computing systems. The database module uses Neo4J and requires us to have either a local or remote instance running it. The connection of the JVM to the Neo4J is made using the BOLT protocol on the network port: 7687. The JSON format was chosen as the way to retrieve the information from the DBLP database using the API due to it being lightweight and having overall great flexibility. The Neo4J database is queried using "
Cypher" which is its standard query language. The application was built using the Maven tool and uses the Neo4J driver and JSON maven repositories. Finally, we use the java.net package in order to establish an HTTP connection with the DBLP API.

@@

\section{Future Work}
The reader of this article has to keep in mind that this project was developed in one month throughout the writer's internship with INESC-ID. Because of this there are many aspects of the current BibTrek implementation that ought to be further engineered and developed. To begin with, one of the obvious aspects to further develop would be to fetch information from more than one web based library. At the current moment only the DBLP is being used. Finally, while the ArXiV API is free to use, IEEE Xplore requires the use of a key attributed to its developers. Another aspect that should be considered is the use of dynamic attributes since, at the moment, any block of data that is fetched has some of its attributes unused because, we adhere to a fixed attribute standard when adding data to the database. At the current moment the only nodes being added to the database are either Authors or Publications. We should consider adding Companies, Foundations, Organizations, Universities and other Institutions that authors are or have been linked with in the past, Keywords/Subjects and any other relevant information for the reader. It is worth being said that nodes being created ought to be the most common set of information between the data that is being stored in the different databases that BibTrek will be using. Finally, along with more diverse nodes, each one of them should have a vast array of arguments in order to better categorize the information being added. Furthermore, at the current moment BibTrek allows the user to add duplicated information. Also, to infer better relations between the nodes already stored in the database we should use their URL attribute to download the publication's PDF and use a text reading tool such as iText in order to read its references and through them relate which node references each node. This way we can have a richer graph and understand which of the papers is the most important building block to learn about a certain subject. Obviously a check should be added in the Java code that compares if the information that is trying to be added has been put there already. Finally, we are not able to query our Neo4J graph database through the terminal console. The work to be done regarding this topic is developing the option of querying the database through a user input choice from a vast array of specific functions that manipulate the information present there, displaying relevant information about the current status of the data to the user we the intent on aiding its research process. An example of a query would be getting the most referenced paper by all the papers presently on the database with respect to a certain subject or given the current paper title that references one of the said papers.

\section{Conclusion}
The BibTrek prototype the way it was implemented allows us to fully query the DBLP database and acquire diverse information about the subject matter. Currently it presents a fully functional rich user interface allowing the user to insert all obtained information into the Neo4J graph database. We are able to construct a graph with some relevant node information and the relations between these nodes being able to infer which authors wrote each paper. This project's potential is related with the strength of us being able to use different databases to our advantage. This way we would be able to add even more data and create a very complex but informative graph. There is also some work to be done in inferring more information than the one being currently inferred about the retrieved data from DBLP adding more nodes and attributes to the graph representation. Finally, we should crawl the database publications' PDF texts in order to add a relationship between publication nodes that reference one another in the database.
